---
title: "SVAP ASSIGMENT - DAILY MARKET ARRIVALS AND ONION PRICES"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
  word_document: default
---

#Step-1 : Frame
  
    The following analysis of the Daily Market Arrivals and Onion Prices is done to answer the following two questions.
    1. Which state has the highest sale of onions in a day
    2. Predict the price of onion for the next 30 days in that state,
    
#Step-2 : Acquire

    Lets get the data from the nhrdf data source starting from year 2016 through 2017.The link for the data is as below
    
    http://nhrdf.org/en-us/DailyWiseMarketArrivals
    
```{r AcquireChunk}
library("rvest")
setwd("F:\\GLIMS-PGPBDA\\Assignments\\SVAP-Assignment\\Assignment-1\\")
pg.out = read_html("DailyWiseMarketArrivals_htm_2017.htm")
pg.table = pg.out %>% html_node("#dnn_ctr966_DailyWiseMarketArrivals_GridView1") %>% html_table
df_2017 = pg.table

```

#Step-3 : Refine

In this section, the following actions are done.
1. Change the Column Names
2. Remove the Total Row in the last.
3. Convert the Data types of Date , Price(Min) , Price (Max) , Price (Mode)
4. Split the Market Column into two different columns holding the City and State
5. Have unique name for the Telangana State
6. Cleanup data to ensure that you have state for all cities.

``` {r Refine}
library(dplyr)
library(tidyr)
newColNames = c('Date','Market','Arr Qty','Min Price','Max Price','Modal Price')
colnames(df_2017) = newColNames

df_2017 = df_2017 %>% filter(Market != "Total")
df_2017$`Max Price` = as.numeric(df_2017$`Max Price`)
df_2017$`Min Price` = as.numeric(df_2017$`Min Price`)
df_2017$`Modal Price` = as.numeric(df_2017$`Modal Price`)
df_2017$Date = as.Date(df_2017$Date, format = '%d/%B/%Y')
str(df_2017)

library(stringr)
df_2017$Market <- str_replace_all(df_2017$Market, "BANGALORE", "BANGALORE(KNT)" )
df_2017$Market <- str_replace_all(df_2017$Market, "BHOPAL", "BHOPAL(MP)" )
df_2017$Market <- str_replace_all(df_2017$Market, "CHANDIGARH", "CHANDIGARH(PUN)" )
df_2017$Market <- str_replace_all(df_2017$Market, "CHENNAI", "CHENNAI(TN)" )
df_2017$Market <- str_replace_all(df_2017$Market, "DELHI", "DELHI(DL)" )
df_2017$Market <- str_replace_all(df_2017$Market, "GUWAHATI", "GUWAHATI(ASSAM)" )
df_2017$Market <- str_replace_all(df_2017$Market, "HYDERABAD", "HYDERABAD(TG)" )
df_2017$Market <- str_replace_all(df_2017$Market, "JAIPUR", "RAIPUR(RAJASTHAN)" )
df_2017$Market <- str_replace_all(df_2017$Market, "JAMMU", "JAMMU(JK)" )
df_2017$Market <- str_replace_all(df_2017$Market, "LUCKNOW", "LUCKNOW(UP)" )
df_2017$Market <- str_replace_all(df_2017$Market, "MUMBAI", "MUMBAI(MS)" )
df_2017$Market <- str_replace_all(df_2017$Market, "NAGPUR", "NAGPUR(MS)" )
df_2017$Market <- str_replace_all(df_2017$Market, "PATNA", "PATNA(BH)" )
df_2017$Market <- str_replace_all(df_2017$Market, "KOLKATA", "KOLKATA(WB)" )
df_2017 = df_2017 %>%
      mutate(Market1 = Market) %>%
      separate(Market1, c("City", "State"), sep = "\\(")
df_2017$State = df_2017$State %>% str_replace("\\)","")
df_2017$State <- str_replace_all(df_2017$State, "Telangana", "TG" )
df_2017$State <- str_replace_all(df_2017$State, "TELANGANA", "TG" )

```

#Step-4 : Transform

  1. Group the data by State and find the sum of the quantity of all days and find the state which has maximum Quantity
```{r}
df_2017_Sum= df_2017 %>% group_by(State) %>% summarise(Qty_Day = sum(`Arr Qty`))
df_2017_Sum[which.max(df_2017_Sum$Qty_Day),]
```


#Step-5 : Explore

```{r}
library(ggplot2)
library(plotly)
ggplot(df_2017_Sum) + aes(State,weight = Qty_Day) + geom_bar()
```

#Step-6 : Model

  Predicting the Future Sales Quantity ( for 30 days )

```{r}
library("rstan")
library("dplyr")
df_2017_State = df_2017 %>% filter(df_2017$State == "MS") %>% select(Date, `Arr Qty`) %>%  arrange(Date)
ggplot(df_2017_State) + aes(Date,`Arr Qty`) + geom_line()
str(df_2017_State)
library("prophet")
colnames(df_2017_State) <- c('ds', 'y')
prophetObject <- prophet(df_2017_State)
futuredataFrame <- make_future_dataframe(prophetObject, periods = 30, freq = 'd', include_history = FALSE )
forecastData <- predict(prophetObject, futuredataFrame)
plot(prophetObject, forecastData)
prophet_plot_components(prophetObject, forecastData)
```

#Step-6 : Insight/Communicate

```{r}
library(ggmap)
Cities = unique(df_2017$City)
CitiesGeoLoc = geocode(Cities)
dfGeoLoc = bind_cols(df_2017_Sum$City,CitiesGeoLoc)
ggplot(dfGeoLoc) + aes(lon, lat) + geom_point() + coord_map()
IndiaMap <- get_map("India", maptype = "watercolor", source = "stamen", zoom = 5)
ggmap(IndiaMap) + geom_point(data = dfGeoLoc,aes(lon,lat))
```