---
title: "SantoshAgastyaraju_SVAP_Asmt_R3"
author: "Santosh Agastyaraju"
date: "July 8, 2017"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This case study is Monthly production central statistics of food and beverages from year 1997-2011. The data is in the csv format.

#Step-1: Frame the Problem: Identify the key question are you trying to answer

  1. Predict the number of calls KCC will receive in 2017 on daily basis
  
#Step-2: Acquire the Data: Get the dataset to answer the question.
  
  Acquire the data from the csv file and load it.
  
``` {r DataRead}
setwd="F:\\GLIMS-PGPBDA\\Assignments\\SVAP-Assignment\\Assignment-3\\"
rawdata = read.csv("Production-Department_of_Agriculture_and_Cooperation_1.csv")
str(rawdata)
```

#Step-3: Refine the Data: Do the basic refinement to clean up the dataset.

  Have only the data related to area wise food grain production

```{r}
library(tidyr)
rawdata = rawdata[grepl('Agricultural Production Foodgrains Area ',rawdata$Particulars),]
rawdata = rawdata[!grepl('Agricultural Production Foodgrains Area 5 Yr',rawdata$Particulars),]
rawdata = rawdata[,-2:-14]
str(rawdata)
```

#Step-4: Transform the Data: Do the transformation needed for the dataset.

  Do the following transformations in the data.
  Split the Particulars column name and have the State in seperate column

```{r}
library(splitstackshape)
rawdata$Particulars = as.character(rawdata$Particulars)
rawdata = cSplit(rawdata, "Particulars", " ")
rawdata = rawdata[ , -c("Particulars_1","Particulars_2","Particulars_3","Particulars_4")]
 rawdata$State = paste(rawdata$Particulars_5,rawdata$Particulars_6)
 rawdata = rawdata[ , -c("Particulars_5","Particulars_6","X3.2014")]
 rawdata$State = sub("NA","",rawdata$State)
 
 rawdata$TotalStats = rawdata$X3.2004+rawdata$X3.2005+rawdata$X3.2006+rawdata$X3.2007+rawdata$X3.2008+rawdata$X3.2009+rawdata$X3.2010+rawdata$X3.2011+rawdata$X3.2012+rawdata$X3.2013
 rawdata
```

#Step-5: Explore the Data: Create the 3 - 4 individual visualisation that explore the dataset.

  Exploring the data by creating the visualisations
  
  
```{r}
library(ggplot2)
library(plotly)
library(knitr)
library(DT)

ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2004 , color = rawdata$State) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2005) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2006) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2007) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2008) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2009) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2010) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2011) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2012) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$X3.2013) + geom_bar()
ggplot(rawdata) + aes(rawdata$State,weight = rawdata$TotalStats) + geom_bar()

datatable(rawdata,option = list(pagelength = 5))

library(ggplot2)
plot1 = ggplot(rawdata) + aes(rawdata$State,rawdata$TotalStats , color=rawdata$State ) + geom_point()

library(plotly)

ggplotly(plot1)

library(crosstalk)
library(d3scatter)

shared_rawdata <- SharedData$new(rawdata)

bscols(
  list(
    filter_checkbox("State", "StateSelect", shared_rawdata, ~State, inline = TRUE),
    filter_slider("TotalStats", "TotalStats", shared_rawdata, ~TotalStats, width = "100%")
  ),
  d3scatter(shared_rawdata, ~TotalStats, ~X3.2004, ~State, width="100%", height=300),
  d3scatter(shared_rawdata, ~TotalStats, ~X3.2005, ~State, width="100%", height=300)
)

```